\twolines
\begin{abstract}\normalsize
    车站连锁能够保证行车安全、提高运行效率，当下，在车站联锁系统中，
    计算机联锁已然成为主流。而计算机联锁培训系统就是用于计算机联锁教育培训的
    产品。而软件仿真则是最普遍的一种培训系统的模式。但传统的软件仿真计算机联锁
    培训系统存在着教学效率低、需要软件分发、软件运行环境限制、难以管理等问题。

    本设计使用IT行业内最新的软件设计技术，设计了一款基于Web、分布式、可扩展、
    高性能、高度灵活的计算机联锁培训系统，使用了极其高效的 Rust 程序设计语言，
    采用异步编程范式作为服务端，使用React.js和Two.js来渲染web端。
    设计为Web应用使得本设计不需要拘束于任何操作系统。
    并解决了传统软件计算机联锁培训系统的C/S模式的其他种种缺点，提高了培训效率。

    根据分布式的架构，本文使用了相应的技术来实现各层的各个模块，以及各个模块
    之间的耦合。在最后，对本设计进行了测试，以证明本设计实现了设计所要求的目标。
\end{abstract}
\textbf{关键字：} 分布式系统；Web应用；GraphQL；Rust程序设计语言；计算机联锁
\newpage

\twolines
\noindent\textbf{\large{Title}} ~ \uline{\large\hautengtitle\hfill}
\\
% \hangindent 4em \uline{\hautengtitle\hfill}

\renewcommand{\abstractname}{\flushleft\large{Abstract}}
\begin{abstract}\normalsize
    \noindent
    Computer-based interlocking has become the mainstream in station interlocking systems, which can ensure the safety of traffic and improve operational efficiency.
    The computer-based interlocking training system is a product used for computer-based interlocking education and training.
    Software simulation is the most common mode of training system. However, the traditional software simulation computer-based
    interlocking training system has problems such as low teaching efficiency, the need for software distribution, software operating environment restrictions,
    and difficulty in management.

    This design uses the latest software design technology within the IT industry to design a web-based, distributed, scalable, high-performance,
    and highly flexible computer-based interlocking training system that uses the extremely efficient Rust programming language,
    an asynchronous programming paradigm as the server side, and React.js and Two.js to render the web side.
    Designed for web applications makes this design not bound to any operating system.
    It also solves various other drawbacks of the C/S model of traditional software computer-based interlocking training system and improves the training efficiency.

    According to the distributed architecture, this paper uses the appropriate technology to implement each module of each layer and the coupling between each module.
    At the end, the design is tested to prove that it achieves the objectives required by the design.
\end{abstract}
\textbf{Keywords：} Distributed systems；Web application；GraphQL；Rust Programming Language；Computer-based interlocking
\newpage